---
title: "ARCH_Model_Lab3"
author: "Kelvin Nyongesa"
date: "2023-05-30"
output: html_document
---

Import the libraries
```{r}
library(readxl)
library(rugarch)
```

Loading the Data 
```{r}
cbkdata<-read_excel("C:/Users/DELL LATITUDE E7270/Documents/4.1/FTSA/FTSA_LEC_LAB/investingcom.csv.xlsx")
head(cbkdata)
```


Converting the data into univariate
```{r}
library(tidyverse)

# Convert date variable to Date class
cbkdata$Date <- as.Date(cbkdata$Date, format = "%m/%d/%Y")

# Create a new data frame to store the log returns

log_returns <- data.frame(
  Returns = c(
    diff(log(cbkdata$USD)),
    diff(log(cbkdata$POUND)),
    diff(log(cbkdata$EURO)),
    diff(log(cbkdata$YEN)),
    diff(log(cbkdata$RAND))
  )
)

# Print the returns data frame
head(log_returns)

```


Is there any serial correlation in the log return series? How do check using ACF and PACF plots and the Ljung-Box statistics?
```{r}
# Load required packages
library(tseries)

# ACF plot
acf(log_returns)

# PACF plot
pacf(log_returns)

```

Using the Ljung Box check the serial Correlation

```{r}
# Perform Ljung-Box test on the log returns
ljung_box_test <- Box.test(log_returns, lag = 10, type = "Ljung-Box")

# Print the Ljung-Box test results
print(ljung_box_test)

```
Based on the extremely small p-value of less than 2.2e-16, we can conclude that there is strong evidence of serial correlation in the log return data. The p-value represents the probability of obtaining the observed test statistic under the null hypothesis of no serial correlation. In this case, the p-value is practically zero, indicating that the observed test statistic is highly unlikely to occur if there is no serial correlation.

Therefore, we reject the null hypothesis of no serial correlation and conclude that there is a significant presence of serial correlation in the log return data.


ARCH Effect using Ljung-Box test
```{r}
library(forecast)

# Fit an ARCH model to the log returns
arch_model <- garch(log_returns)

# Obtain the squared residuals
squared_residuals <- arch_model$residuals^2

# Perform Ljung-Box test on the squared residuals
ljung_box_test <- Box.test(squared_residuals, lag = 10, type = "Ljung-Box")

# Print the Ljung-Box test results
print(ljung_box_test)
```

Based on the p-value of 0.3831 obtained from the Ljung-Box test on the squared residuals, we do not have sufficient evidence to conclude the presence of an ARCH effect in the daily log returns. The p-value is above the typical significance level of 0.05, indicating that we fail to reject the null hypothesis of no ARCH effect.

Therefore, based on the given p-value, we do not have significant evidence to suggest the presence of autocorrelation in the squared residuals and, consequently, no ARCH effect in the daily log returns.



